---
title: "How is personality pathology related to negative perceptions of others?"
author: "Michael Carnovale, Vina Goghari, Erika Carlson"
date: SRP 2021
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_control: true
    number_sections: true
---
# Load Required Packages

```{r, message=F, warning = F}

library(psych) # For descriptives
library(jtools) # For regression model summaries
library(inspectdf) # For EDA
library(summarytools) # For EDA
library(DataExplorer) # For EDA
library(TripleR) # For estimating Social Relations Model
library(stringi) # Data wrangling
library(tidymodels) # For various tidyverse functions
library(lavaan) # SEM
library(DescTools) # To implement Jonckheere's trend test
library(ggplot2) # Plots


```

<style>
pre {
  overflow-x: auto;
}
pre code {
  word-wrap: normal;
  white-space: pre;
}
</style>

```{r}


installed.packages()[names(sessionInfo()$otherPkgs), "Version"]

```

```{r}
#### Import data ####
# Baseline data
df_baseline = read.csv("https://raw.githubusercontent.com/michaelcarnovale/SRP-2021-Poster/main/Data/Baseline_Data_Carnovale.csv", 
header = T)
df_baseline = df_baseline[,-1] # Removing extra column

# Post-interaction round robin data
df_end = read.csv("https://raw.githubusercontent.com/michaelcarnovale/SRP-2021-Poster/main/Data/RoundRobin_Data_Carnovale.csv",
                  header = T)
df_end = df_end[,-1] # Removing extra column

```

# Data Cleaning/Structuring/Management
```{r, warning = F}
#### Recoding variables of interest ####
df_end$letter = df_end$letter - 1
names(df_end) = c("Study_ID", "Letter", "Session_ID",
                  "ext1.a", "con1.a", "opn1.a", "agr1.a", "neu1.a", "agr2.a", "neu2.a", "ext2.a", "con2.a", "opn2.a",
                  "ext1.b", "con1.b", "opn1.b", "agr1.b", "neu1.b", "agr2.b", "neu2.b", "ext2.b", "con2.b", "opn2.b",
                  "ext1.c", "con1.c", "opn1.c", "agr1.c", "neu1.c", "agr2.c", "neu2.c", "ext2.c", "con2.c", "opn2.c",
                  "ext1.d", "con1.d", "opn1.d", "agr1.d", "neu1.d", "agr2.d", "neu2.d", "ext2.d", "con2.d", "opn2.d",
                  "ext1.e", "con1.e", "opn1.e", "agr1.e", "neu1.e", "agr2.e", "neu2.e", "ext2.e", "con2.e", "opn2.e",
                  "letter")

df_end$Session_ID = as.numeric(df_end$Session_ID) # Making a 'perceiver' variable
df_end$perceiver = df_end$Session_ID + (df_end$letter/10)
df_end = df_end %>%
  filter(Session_ID !=999, Session_ID !=2999) # Removing 'test' sessions run by RAs

#### Formatting the round robin data from wide to long ####
df_end = df_end %>%
  distinct(perceiver, .keep_all = T)
df_end = reshape(df_end,
                 varying = list(c("ext1.a", "ext1.b", "ext1.c", "ext1.d", "ext1.e"),
                                c("ext2.a", "ext2.b", "ext2.c", "ext2.d", "ext2.e"),
                                c("con1.a", "con1.b", "con1.c", "con1.d", "con1.e"),
                                c("con2.a", "con2.b", "con2.c", "con2.d", "con2.e"),
                                c("agr1.a", "agr1.b", "agr1.c", "agr1.d", "agr1.e"),
                                c("agr2.a", "agr2.b", "agr2.c", "agr2.d", "agr2.e"),
                                c("neu1.a", "neu1.b", "neu1.c", "neu1.d", "neu1.e"),
                                c("neu2.a", "neu2.b", "neu2.c", "neu2.d", "neu2.e"),
                                c("opn1.a", "opn1.b", "opn1.c", "opn1.d", "opn1.e"),
                                c("opn2.a", "opn2.b", "opn2.c", "opn2.d", "opn2.e")),
                 direction = "long",
                 v.names = c("ext1", "ext2", "con1", "con2", "agr1", "agr2", "neu1", "neu2", "opn1", "opn2"),
                 idvar = c("Session_ID", "perceiver"),
                 timevar = "letter")


#### Scoring variables ####

## Target variable
df_end$target = df_end$Session_ID + (df_end$letter/10)

## TIPI
df_end = df_end %>%
  mutate(ext1 = recode(ext1,
                       '1  Not at all' = '1',
                       '7  Extremely' = '7'),
         con1 = recode(con1,
                       '1  Not at all' = '1',
                       '7  Extremely' = '7'),
         agr1 = recode(agr1,
                       '1  Not at all' = '1',
                       '7  Extremely' = '7'),
         neu1 = recode(neu1,
                       '1  Not at all' = '1',
                       '7  Extremely' = '7'),
         opn1 = recode(opn1,
                       '1  Not at all' = '1',
                       '7  Extremely' = '7'),
         ext2 = recode(ext2,
                       '1  Not at all' = '1',
                       '7  Extremely' = '7'),
         con2 = recode(con2,
                       '1  Not at all' = '1',
                       '7  Extremely' = '7'),
         agr2 = recode(agr2,
                       '1  Not at all' = '1',
                       '7  Extremely' = '7'),
         neu2 = recode(neu2,
                       '1  Not at all' = '1',
                       '7  Extremely' = '7'),
         opn2 = recode(opn2,
                       '1  Not at all' = '1',
                       '7  Extremely' = '7')) %>%
  mutate(ext1 = as.numeric(ext1),
         con1 = as.numeric(con1),
         agr1 = as.numeric(agr1),
         neu1 = as.numeric(neu1),
         opn1 = as.numeric(opn1),
         ext2 = as.numeric(ext2),
         con2 = as.numeric(con2),
         agr2 = as.numeric(agr2),
         neu2 = as.numeric(neu2),
         opn2 = as.numeric(opn2)) 



## PID-5-BF (self-report)
df_baseline_names = names(df_baseline)
df_baseline[,df_baseline_names] = lapply(df_baseline[,df_baseline_names], as.numeric)
df_baseline = df_baseline %>%
  mutate(negativeaffect = rowMeans(select(., PID8_1, PID9_1, PID10_1, PID11_1, PID15_1), na.rm = T),
         detachment = rowMeans(select(., PID4_1, PID13_1, PID14_1, PID16_1, PID18_1), na.rm = T),
         antagonism = rowMeans(select(., PID17_1, PID19_1, PID20_1, PID22_1, PID25_1), na.rm = T),
         disinhibition = rowMeans(select(., PID1_1, PID2_1, PID3_1, PID5_1, PID6_1), na.rm = T),
         psychoticism = rowMeans(select(., PID7_1, PID12_1, PID21_1, PID23_1, PID24_1), na.rm = T))

```



# Estimating Social Relations Models

The Social Relations Model was estimated for each TIPI item that was rated in the round robin design.
```{r, warning = F}
#### Round robin models ####
neu1.rr = RR(neu1 ~ perceiver*target|Session_ID, data = df_end, na.rm = T)
neu2.rr = RR(neu2 ~ perceiver*target|Session_ID, data = df_end, na.rm = T)
ext1.rr = RR(ext1 ~ perceiver*target|Session_ID, data = df_end, na.rm = T)
ext2.rr = RR(ext2 ~ perceiver*target|Session_ID, data = df_end, na.rm = T)
opn1.rr = RR(opn1 ~ perceiver*target|Session_ID, data = df_end, na.rm = T)
opn2.rr = RR(opn2 ~ perceiver*target|Session_ID, data = df_end, na.rm = T)
agr1.rr = RR(agr1 ~ perceiver*target|Session_ID, data = df_end, na.rm = T)
agr2.rr = RR(agr2 ~ perceiver*target|Session_ID, data = df_end, na.rm = T)
con1.rr = RR(con1 ~ perceiver*target|Session_ID, data = df_end, na.rm = T)
con2.rr = RR(con2 ~ perceiver*target|Session_ID, data = df_end, na.rm = T)



## Putting perceiver effects in separate dataframe
df_p = neu1.rr$effects[,c(1, 3)]
df_p = merge(df_p, neu2.rr$effects[,c(1, 3)], by = "id")
df_p = merge(df_p, ext1.rr$effects[,c(1, 3)], by = "id")
df_p = merge(df_p, ext2.rr$effects[,c(1, 3)], by = "id")
df_p = merge(df_p, opn1.rr$effects[,c(1, 3)], by = "id")
df_p = merge(df_p, opn2.rr$effects[,c(1, 3)], by = "id")
df_p = merge(df_p, agr1.rr$effects[,c(1, 3)], by = "id") 
df_p = merge(df_p, agr2.rr$effects[,c(1, 3)], by = "id")
df_p = merge(df_p, con1.rr$effects[,c(1, 3)], by = "id")
df_p = merge(df_p, con2.rr$effects[,c(1, 3)], by = "id")

df_end_names = names(df_end)
df_end[,df_end_names] = lapply(df_end[,df_end_names], as.numeric)
test = merge(df_end, df_baseline, by = "Study_ID")

df_baseline2 = test %>%
  dplyr::rename(id = perceiver) %>%
  select(id, Study_ID, negativeaffect, detachment, antagonism, disinhibition, psychoticism,
         PID1_1:PID25_1, Session_ID, Age, Gender, Ethnicity)

df_full = merge(df_p, df_baseline2, by = "id")
df_full = df_full %>%
  distinct(id, .keep_all = T) %>%
  filter(Session_ID!=2067) # Coding errors in this session

```

```{r}
##### Making total score ######
df_full = df_full %>%
  mutate(total = rowMeans(select(., negativeaffect, detachment, antagonism, disinhibition, psychoticism), 
                          na.rm = T))
```

# Exploratory Data Analysis (Self-Report)
```{r}
## Descriptive stats (IVs only)
df_full %>% 
  select(negativeaffect, detachment, antagonism, disinhibition, psychoticism, total, Age) %>% 
  describe(quant = c(.25, .75))
df_full %>% 
  select(PID1_1:PID25_1, Gender) %>% 
  freq()

## Univariate visualizations
# Categorical variables
df_full %>% 
  select(PID1_1:PID25_1, Gender) %>% 
  mutate_if(is.numeric, as.factor) %>%
  inspect_cat() %>%
  show_plot()
df_full %>% 
  select(PID1_1:PID25_1, Gender) %>% 
  mutate_if(is.numeric, as.factor) %>%
  plot_bar()
# Numeric variables
df_full %>%
  select(negativeaffect, detachment, antagonism, disinhibition, psychoticism, total, Age) %>%
  plot_histogram()
df_full %>%
  select(negativeaffect, detachment, antagonism, disinhibition, psychoticism, total, Age) %>%
  plot_density()
```


# Regression Models (Self-Report Data)
```{r}
## Creating PCA variable for pos/neg perceiver effects
test_pca = df_full %>%
  select(neu1.a:con2.a) %>%
  principal(nfactors = 1)

df_full$perceiver_effect = test_pca$scores

```

```{r}
## Making function to estimate models and correct p-values
model.function = function(var1, var2, var3, var4, var5, var6, data){
  m1 = lm(perceiver_effect ~ var1, data = data) %>% summ(scale = T, robust = T, confint = T, digits = 3) # Robust SEs
  m2 = lm(perceiver_effect ~ var2, data = data) %>% summ(scale = T, robust = T, confint = T, digits = 3)
  m3 = lm(perceiver_effect ~ var3, data = data) %>% summ(scale = T, robust = T, confint = T, digits = 3)
  m4 = lm(perceiver_effect ~ var4, data = data) %>% summ(scale = T, robust = T, confint = T, digits = 3)
  m5 = lm(perceiver_effect ~ var5, data = data) %>% summ(scale = T, robust = T, confint = T, digits = 3)
  m6 = lm(perceiver_effect ~ var6, data = data) %>% summ(scale = T, robust = T, confint = T, digits = 3)
  
  pval = c(rep(NA, 6)) # Vector to hold p-values associated with each b1 coefficient
  pval[1] = m1$coeftable[2, 5]
  pval[2] = m2$coeftable[2, 5]
  pval[3] = m3$coeftable[2, 5]
  pval[4] = m4$coeftable[2, 5]
  pval[5] = m5$coeftable[2, 5]
  pval[6] = m6$coeftable[2, 5]
  
  print(m1) # Printing model output
  print(m2)
  print(m3)
  print(m4)
  print(m5)
  print(m6)
  
  p.adjust(pval, method = "BH") # Adjusting b1 p-values with BH method
  
}

## Bivariate relations
model.function(df_full$negativeaffect, df_full$detachment, df_full$antagonism, 
               df_full$disinhibition, df_full$psychoticism, df_full$total, df_full) # Note the order of variables




```

# Cleaning and Scoring Informant Data
```{r}
df_inf = read.csv("https://raw.githubusercontent.com/michaelcarnovale/SRP-2021-Poster/main/Data/Informant_Data_Carnovale.csv",
                  header = T)
df_inf = df_inf[,-1] # Removing extra column

df_inf$Informant_ID = stri_trim_both(df_inf$Informant_ID)
df_inf$Informant_ID = stri_sub(df_inf$Informant_ID, 3)
```

```{r}

## Scoring
df_inf = df_inf %>%
  mutate(pid1 = recode(informant_pid_1_1,
                       'Very False or Often False' = '1',
                       'Sometimes or Somewhat False' = '2',
                       'Sometimes or Somewhat True' = '3',
                       'Very True or Often True' = '4'),
         pid2 = recode(informant_pid_2_1,
                       'Very False or Often False' = '1',
                       'Sometimes or Somewhat False' = '2',
                       'Sometimes or Somewhat True' = '3',
                       'Very True or Often True' = '4'),
         pid3 = recode(informant_pid_3_1,
                       'Very False or Often False' = '1',
                       'Sometimes or Somewhat False' = '2',
                       'Sometimes or Somewhat True' = '3',
                       'Very True or Often True' = '4'),
         pid4 = recode(informant_pid_4_1,
                       'Very False or Often False' = '1',
                       'Sometimes or Somewhat False' = '2',
                       'Sometimes or Somewhat True' = '3',
                       'Very True or Often True' = '4'),
         pid5 = recode(informant_pid_5_1,
                       'Very False or Often False' = '1',
                       'Sometimes or Somewhat False' = '2',
                       'Sometimes or Somewhat True' = '3',
                       'Very True or Often True' = '4'),
         pid6 = recode(informant_pid_6_1,
                       'Very False or Often False' = '1',
                       'Sometimes or Somewhat False' = '2',
                       'Sometimes or Somewhat True' = '3',
                       'Very True or Often True' = '4'),
         pid7 = recode(informant_pid_7_1,
                       'Very False or Often False' = '1',
                       'Sometimes or Somewhat False' = '2',
                       'Sometimes or Somewhat True' = '3',
                       'Very True or Often True' = '4'),
         pid8 = recode(informant_pid_8_1,
                       'Very False or Often False' = '1',
                       'Sometimes or Somewhat False' = '2',
                       'Sometimes or Somewhat True' = '3',
                       'Very True or Often True' = '4'),
         pid9 = recode(informant_pid_9_1,
                       'Very False or Often False' = '1',
                       'Sometimes or Somewhat False' = '2',
                       'Sometimes or Somewhat True' = '3',
                       'Very True or Often True' = '4'),
         pid10 = recode(informant_pid_10_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4'),
         pid11 = recode(informant_pid_11_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4'),
         pid12 = recode(informant_pid_12_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4'),
         pid13 = recode(informant_pid_13_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4'),
         pid14 = recode(informant_pid_14_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4'),
         pid15 = recode(informant_pid_15_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4'),
         pid16 = recode(informant_pid_16_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4'),
         pid17 = recode(informant_pid_17_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4'),
         pid18 = recode(informant_pid_18_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4'),
         pid19 = recode(informant_pid_19_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4'),
         pid20 = recode(informant_pid_20_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4'),
         pid21 = recode(informant_pid_21_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4'),
         pid22 = recode(informant_pid_22_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4'),
         pid23 = recode(informant_pid_23_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4'),
         pid24 = recode(informant_pid_24_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4'),
         pid25 = recode(informant_pid_25_1,
                        'Very False or Often False' = '1',
                        'Sometimes or Somewhat False' = '2',
                        'Sometimes or Somewhat True' = '3',
                        'Very True or Often True' = '4')) %>%
  mutate(pid1 = as.numeric(pid1),
         pid2 = as.numeric(pid2),
         pid3 = as.numeric(pid3),
         pid4 = as.numeric(pid4),
         pid5 = as.numeric(pid5),
         pid6 = as.numeric(pid6),
         pid7 = as.numeric(pid7),
         pid8 = as.numeric(pid8),
         pid9 = as.numeric(pid9),
         pid10 = as.numeric(pid10),
         pid11 = as.numeric(pid11),
         pid12 = as.numeric(pid12),
         pid13 = as.numeric(pid13),
         pid14 = as.numeric(pid14),
         pid15 = as.numeric(pid15),
         pid16 = as.numeric(pid16),
         pid17 = as.numeric(pid17),
         pid18 = as.numeric(pid18),
         pid19 = as.numeric(pid19),
         pid20 = as.numeric(pid20),
         pid21 = as.numeric(pid21),
         pid22 = as.numeric(pid22),
         pid23 = as.numeric(pid23),
         pid24 = as.numeric(pid24),
         pid25 = as.numeric(pid25),
         Informant_ID = as.factor(Informant_ID))


df_inf = df_inf %>%
  select(Informant_ID, pid1:pid25)


df_inf = df_inf %>%
  mutate(negativeaffect_inf = rowMeans(select(., pid8, pid9, pid10, pid11, pid15), na.rm = T),
         detachment_inf = rowMeans(select(., pid4, pid13, pid14, pid16, pid18), na.rm = T),
         antagonism_inf = rowMeans(select(., pid17, pid19, pid20, pid22, pid25), na.rm = T),
         disinhibition_inf = rowMeans(select(., pid1, pid2, pid3, pid5, pid6), na.rm = T),
         psychoticism_inf = rowMeans(select(., pid7, pid12, pid21, pid23, pid24), na.rm = T))

df_inf = df_inf %>%
  drop_na(negativeaffect_inf:psychoticism_inf)


# Randomly select one informant if target has more than one informant
set.seed(2021)
df_inf = df_inf %>%
  group_by(Informant_ID) %>%
  sample_n(1) %>% 
  ungroup()

df_inf = df_inf %>%
  mutate(total_inf = rowMeans(select(., negativeaffect_inf, detachment_inf, antagonism_inf, disinhibition_inf, 
                                     psychoticism_inf), 
                          na.rm = T))
```
# Merging with Target Data
```{r}
###### Merging data with target data #######
df_inf = df_inf %>%
  rename(Study_ID = Informant_ID)
df_full2 = merge(df_full, df_inf, by = "Study_ID")
```

# Exploratory Data Analysis (Informant-Report)

```{r}
df_full2 %>% 
  select(negativeaffect_inf, detachment_inf, antagonism_inf, disinhibition_inf, psychoticism_inf, total_inf) %>% 
  describe(quant = c(.25, .75))
# Univariate visualizations
df_full2 %>%
  select(negativeaffect_inf, detachment_inf, antagonism_inf, disinhibition_inf, psychoticism_inf, total_inf) %>%
  plot_histogram()
df_full2 %>%
  select(negativeaffect_inf, detachment_inf, antagonism_inf, disinhibition_inf, psychoticism_inf, total_inf) %>%
  plot_density()
```

# Regression Models (Informant-Report Data)
```{r}
## Univariate relations (note order of variables)
model.function(df_full2$negativeaffect_inf, df_full2$detachment_inf, df_full2$antagonism_inf,
               df_full2$disinhibition_inf, df_full2$psychoticism_inf, df_full2$total_inf, df_full2) 

```

# Structural-After-Measurement SEMs
```{r, warning = F}
## Negative Affect
# Self-report
n_model_self = '
naffect =~ PID8_1 + PID9_1 +  PID10_1 + PID11_1 + PID15_1 
pos =~ neu1.a + neu2.a + ext1.a + ext2.a + opn1.a + opn2.a + agr1.a + agr2.a + con1.a + con2.a

pos ~ naffect'
n_out_self = sam(n_model_self, data = df_full, std.lv = T)
summary(n_out_self, ci = T) 

# Informant
n_model_inf = '
naffect =~ pid8 + pid9 +  pid10 + pid11 + pid15 
pos =~ neu1.a + neu2.a + ext1.a + ext2.a + opn1.a + opn2.a + agr1.a + agr2.a + con1.a + con2.a

pos ~ naffect'
n_out_inf = sam(n_model_inf, data = df_full2, std.lv = T)
summary(n_out_inf, fit.measures = T, ci = T) 




## Detachment
# Self-report
det_model_self = '
det =~ PID4_1 + PID13_1 + PID14_1 + PID16_1 + PID18_1 
pos =~ neu1.a + neu2.a + ext1.a + ext2.a + opn1.a + opn2.a + agr1.a + agr2.a + con1.a + con2.a

pos ~ det'
det_out_self = sam(det_model_self, data = df_full, std.lv = T)
summary(det_out_self, fit.measures = T, ci = T) 

# Informant
det_model_inf = '
det =~ pid4 + pid13 + pid14 + pid16 + pid18
pos =~ neu1.a + neu2.a + ext1.a + ext2.a + opn1.a + opn2.a + agr1.a + agr2.a + con1.a + con2.a

pos ~ det'
det_out_inf = sam(det_model_inf, data = df_full2, std.lv = T)
summary(det_out_inf, fit.measures = T, ci = T) 






## Antagonism
# Self-report
ant_model_self = '
ant =~ PID17_1 + PID19_1 + PID20_1 + PID22_1 + PID25_1 
pos =~ neu1.a + neu2.a + ext1.a + ext2.a + opn1.a + opn2.a + agr1.a + agr2.a + con1.a + con2.a

pos ~ ant'
ant_out_self = sam(ant_model_self, data = df_full, std.lv = T)
summary(ant_out_self, fit.measures = T, ci = T) 

# Informant
ant_model_inf = '
ant =~ pid17 + pid19 + pid20 + pid22 + pid25 
pos =~ neu1.a + neu2.a + ext1.a + ext2.a + opn1.a + opn2.a + agr1.a + agr2.a + con1.a + con2.a

pos ~ ant'
ant_out_inf = sam(ant_model_inf, data = df_full2, std.lv = T)
summary(ant_out_inf, fit.measures = T, ci = T) 







## Disinhibition
# Self-report
dis_model_self = '
dis =~ PID1_1 + PID2_1 + PID3_1 + PID5_1 + PID6_1 
pos =~ neu1.a + neu2.a + ext1.a + ext2.a + opn1.a + opn2.a + agr1.a + agr2.a + con1.a + con2.a

pos ~ dis'
dis_out_self = sam(dis_model_self, data = df_full, std.lv = T)
summary(dis_out_self, fit.measures = T, ci = T) 

# Informant
dis_model_inf = '
dis =~ pid1 + pid2 + pid3 + pid5 + pid6
pos =~ neu1.a + neu2.a + ext1.a + ext2.a + opn1.a + opn2.a + agr1.a + agr2.a + con1.a + con2.a

pos ~ dis'
dis_out_inf = sam(dis_model_inf, data = df_full2, std.lv = T)
summary(dis_out_inf, fit.measures = T, ci = T)






## Psychoticism
# Self-report
psych_model_self = '
psych =~ PID7_1 + PID12_1 + PID21_1 + PID23_1 + PID24_1 
pos =~ neu1.a + neu2.a + ext1.a + ext2.a + opn1.a + opn2.a + agr1.a + agr2.a + con1.a + con2.a

pos ~ psych'
psych_out_self = sam(psych_model_self, data = df_full, std.lv = T)
summary(psych_out_self, fit.measures = T, ci = T)

# Informant
psych_model_inf = '
psych =~ pid7 + pid12 + pid21 + pid23 + pid24 
pos =~ neu1.a + neu2.a + ext1.a + ext2.a + opn1.a + opn2.a + agr1.a + agr2.a + con1.a + con2.a

pos ~ psych'
psych_out_inf = sam(psych_model_inf, data = df_full2, std.lv = T)
summary(psych_out_inf, fit.measures = T, ci = T)






## Total scores
# Self-report
total_model_self = '
t =~ negativeaffect + detachment + antagonism + disinhibition + psychoticism
pos =~ neu1.a + neu2.a + ext1.a + ext2.a + opn1.a + opn2.a + agr1.a + agr2.a + con1.a + con2.a

pos ~ t'
total_out_self = sam(total_model_self, data = df_full, std.lv = T)
summary(total_out_self, fit.measures = T, ci = T)

# Informant
total_model_inf = '
t =~ negativeaffect_inf + detachment_inf + antagonism_inf + disinhibition_inf + psychoticism_inf
pos =~ neu1.a + neu2.a + ext1.a + ext2.a + opn1.a + opn2.a + agr1.a + agr2.a + con1.a + con2.a

pos ~ t'
total_out_inf = sam(total_model_inf, data = df_full2, std.lv = T)
summary(total_out_inf, fit.measures = T, ci = T)


## Adjusting p-values of regression coefficients for multiple testing

pvals = c(.372, .235, .063, .267, .001, .392, .005, .098, .119, .195, .010, .079)
p.adjust(pvals, method = "BH") # self-antagonism, self-disinhibition, and self-total still statistically significant



```

# Jonckheere's Trend Test
Tests null hypothesis that k1 = k2 = k3 = kn, where kn is ordinal level 'n'
```{r, warning = F}
# Antagonism items
JonckheereTerpstraTest(df_full$perceiver_effect, ordered(df_full$PID17_1))
JonckheereTerpstraTest(df_full$perceiver_effect, ordered(df_full$PID19_1))
JonckheereTerpstraTest(df_full$perceiver_effect, ordered(df_full$PID20_1))
JonckheereTerpstraTest(df_full$perceiver_effect, ordered(df_full$PID22_1))
JonckheereTerpstraTest(df_full$perceiver_effect, ordered(df_full$PID25_1))

# Disinhibition items
JonckheereTerpstraTest(df_full$perceiver_effect, ordered(df_full$PID1_1))
JonckheereTerpstraTest(df_full$perceiver_effect, ordered(df_full$PID2_1))
JonckheereTerpstraTest(df_full$perceiver_effect, ordered(df_full$PID3_1))
JonckheereTerpstraTest(df_full$perceiver_effect, ordered(df_full$PID5_1))
JonckheereTerpstraTest(df_full$perceiver_effect, ordered(df_full$PID6_1))

# Adjusting p-values for multiple testing
pvals.jt = c(.06882, .8515, .1495, .0001044, .01053, .002552, .004676, .01197, .02221, .1058)
p.adjust(pvals.jt, method = "BH") # Items 22, 25 from antagonism; 1, 2, 3, 5 from disinhibition still statistically significant

```


# Plots
```{r}
ggplot(df_full, aes(negativeaffect, perceiver_effect))+
  geom_smooth(method = "lm", color = "cyan")+
  geom_point(color = "cornflowerblue")+
  labs(x = "Negative Affect (Self)", y = "Perceiver Effect (Neg-Pos)")+
  theme(axis.title = element_text(size = 19))

ggplot(df_full, aes(detachment, perceiver_effect))+
  geom_smooth(method = "lm", color = "antiquewhite1")+
  geom_point(color = "antiquewhite4")+
  labs(x = "Detachment (Self)", y = "Perceiver Effect (Neg-Pos)")+
  theme(axis.title = element_text(size = 19))

ggplot(df_full, aes(antagonism, perceiver_effect))+
  geom_smooth(method = "lm", color = "deeppink1")+
  geom_point(color = "brown2")+
  labs(x = "Antagonism (Self)", y = "Perceiver Effect (Neg-Pos)")+
  theme(axis.title = element_text(size = 19))

ggplot(df_full, aes(disinhibition, perceiver_effect))+
  geom_smooth(method = "lm", color = "darkorchid1")+
  geom_point(color = "darkmagenta")+
  labs(x = "Disinhibition (Self)", y = "Perceiver Effect (Neg-Pos)")+
  theme(axis.title = element_text(size = 19))

ggplot(df_full, aes(psychoticism, perceiver_effect))+
  geom_smooth(method = "lm", color = "darkseagreen2")+
  geom_point(color = "darkolivegreen")+
  labs(x = "Psychoticism (Self)", y = "Perceiver Effect (Neg-Pos)")+
  theme(axis.title = element_text(size = 19))

ggplot(df_full, aes(total, perceiver_effect))+
  geom_smooth(method = "lm", color = "beige")+
  geom_point(color = "darkgreen")+
  labs(x = "Total (Self)", y = "Perceiver Effect (Neg-Pos)")+
  theme(axis.title = element_text(size = 19))

# Informant
ggplot(df_full2, aes(negativeaffect_inf, perceiver_effect))+
  geom_smooth(method = "lm", color = "cyan")+
  geom_point(color = "cornflowerblue")+
  labs(x = "Negative Affect (Inf)", y = "Perceiver Effect (Neg-Pos)")+
  theme(axis.title = element_text(size = 19))

ggplot(df_full2, aes(detachment_inf, perceiver_effect))+
  geom_smooth(method = "lm", color = "antiquewhite1")+
  geom_point(color = "antiquewhite4")+
  labs(x = "Detachment (Inf)", y = "Perceiver Effect (Neg-Pos)")+
  theme(axis.title = element_text(size = 19))

ggplot(df_full2, aes(antagonism_inf, perceiver_effect))+
  geom_smooth(method = "lm", color = "deeppink1")+
  geom_point(color = "brown2")+
  labs(x = "Antagonism (Inf)", y = "Perceiver Effect (Neg-Pos)")+
  theme(axis.title = element_text(size = 19))

ggplot(df_full2, aes(disinhibition_inf, perceiver_effect))+
  geom_smooth(method = "lm", color = "darkorchid1")+
  geom_point(color = "darkmagenta")+
  labs(x = "Disinhibition (Inf)", y = "Perceiver Effect (Neg-Pos)")+
  theme(axis.title = element_text(size = 19))

ggplot(df_full2, aes(psychoticism_inf, perceiver_effect))+
  geom_smooth(method = "lm", color = "darkseagreen2")+
  geom_point(color = "darkolivegreen")+
  labs(x = "Psychoticism (Inf)", y = "Perceiver Effect (Neg-Pos)")+
  theme(axis.title = element_text(size = 19))

ggplot(df_full2, aes(total_inf, perceiver_effect))+
  geom_smooth(method = "lm", color = "beige")+
  geom_point(color = "darkgreen")+
  labs(x = "Total (Inf)", y = "Perceiver Effect (Neg-Pos)")+
  theme(axis.title = element_text(size = 19))

```

